`ggmatplot`: An R package for data visualization on wide-format data

### 2022-03-02 Paper/paper.Rmd
reworked example

wide_df <- tribble(~restaurant, ~person, ~food_rating, ~service_rating, ~ambience_rating, ~overall_rating,
        "R1", "P1", 4, 3, 4, 4,
        "R1", "P2", 4, 5, 4, 4,
        "R1", "P3", 3, 4, 5, 3, 
        "R2", "P1", 2, 4, 4, 3, 
        "R2", "P2", 3, 4, 4, 3)

@@

```{r tab1, echo = FALSE}
table_styling(wide_df, col.names = c("Restaurant", "Person", "Food",
                                     "Service", "Ambience", "Overall"),
              caption = 'Restaurant rating data in "tidy" form') %>% 
  add_header_above(c(" ", " ", "Rating" = 4))
```

```{r tab2, echo = FALSE}
table_styling(long_df, col.names = c("Restauant", "Person", "Rating type", "Rating"),
              caption = 'Restaurant rating data in "molten" form')
```

@@

>>>>

wide_df <- tribble(~restaurant, ~food_rating, ~service_rating, ~ambience_rating, ~overall_rating,
        "R1", 4, 3, 4, 4,
        "R2", 4, 5, 4, 4,
        "R3", 3, 4, 5, 3, 
        "R4", 2, 4, 4, 3, 
        "R5", 3, 4, 4, 3)

@@

```{r tab1, echo = FALSE}
table_styling(wide_df, col.names = c("Restaurant", "Food",
                                     "Service", "Ambience", "Overall"),
              caption = 'Restaurant rating data in "tidy" form') %>% 
  add_header_above(c(" ", "Rating" = 4))
```

```{r tab2, echo = FALSE}
table_styling(long_df, col.names = c("Restauant", "Rating type", "Rating"),
              caption = 'Restaurant rating data in "molten" form')
```

@@

```{r plot1}
library(ggmatplot)
ggmatplot(x = select(wide_df, contains("rating")),
          plot_type = "both",
          xlab = "Restaurant")
```
